Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes

### 2019-12-28 ms/manuscript.Rmd
Write out tables in html
MS Word can read them fine, and less buggy than rtf

# Write out table in rich text format for submitting
# MS as word doc
traits_used %>%
  gt %>%
  fmt_markdown(columns = everything()) %>%
  gt(rowname_col = "trait") %>%
  tab_row_group(
    group = "Sporophyte traits",
    rows = matches("Stipe|Frond|Rhizome|Pinna|Leaf")
  ) %>%
  tab_row_group(
    group = "Gametophyte traits",
    rows = matches("Morphotype|Gemmae|Glands|Hairs")
  ) %>%
  cols_label(
    data_type = "Data type (unit)",
    ecological_significance = "Ecological Significance",
    reference = "Reference(s)"
  ) %>% 
  as_rtf() %>%
  write_lines(here::here("ms/Table_1.rtf"))

@@

# Write out table in rich text format
phylosig_cont_traits_table %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    kval = md("*K*"),
    k_pval = md("*P*(*K*)"),
    lambda_pval = md("*P*(lambda)"),
    lambda = "lambda"
  )  %>% 
  as_rtf() %>%
  write_lines(here::here("ms/Table_2.rtf"))

@@

# Write out table in rich text format
phylosig_binary_traits_table %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    num_present = "Number of presences",
    num_absent = "Number of absences",
    D = md("*D*"),
    prob_random = md("*P*(rnd)"),
    prob_brownian = md("*P*(bm)")
  ) %>% 
  as_rtf() %>%
  write_lines(here::here("ms/Table_3.rtf"))

@@

# Write out table in rich text format
pic_table %>%
gt(rowname_col = "trait") %>%
  cols_label(
    n_contrasts = "Num. constrasts",
    n_pos_con = "Num. pos. constrasts",
    statistic = md("*t*"),
    p.value = md("*P*"),
  ) %>% 
  as_rtf() %>%
  write_lines(here::here("ms/Table_4.rtf"))

@@

# Write out table in rich text format
correlated_evo_test_table %>%
gt(rowname_col = "trait") %>%
  cols_label(
    logL_indep = "LogL(independent)",
    logL_dep = "LogL(dependent)",
    likelihood_ratio = "Likelihood ratio",
    pval = md("*P*"),
  ) %>% 
  as_rtf() %>%
  write_lines(here::here("ms/Table_5.rtf"))

>>>>

# Write out table in html for submitting
# MS as word doc
traits_used %>%
  gt(rowname_col = "trait") %>%
  fmt_markdown(columns = everything()) %>%
  tab_row_group(
    group = "Sporophyte traits",
    rows = matches("Stipe|Frond|Rhizome|Pinna|Leaf")
  ) %>%
  tab_row_group(
    group = "Gametophyte traits",
    rows = matches("Morphotype|Gemmae|Glands|Hairs")
  ) %>%
  cols_label(
    data_type = "Data type (unit)",
    ecological_significance = "Ecological Significance",
    reference = "Reference(s)"
  ) %>% 
  gtsave(here::here("ms/Table_1.html"))

@@

# Write out table in html format
phylosig_cont_traits_table %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    kval = md("*K*"),
    k_pval = md("*P*(*K*)"),
    lambda_pval = md("*P*(lambda)"),
    lambda = "lambda"
  )  %>%
  gtsave(here::here("ms/Table_2.html"))

@@

# Write out table in html
phylosig_binary_traits_table %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    num_present = "Number of presences",
    num_absent = "Number of absences",
    D = md("*D*"),
    prob_random = md("*P*(rnd)"),
    prob_brownian = md("*P*(bm)")
  ) %>% 
  gtsave(here::here("ms/Table_3.html"))

@@

# Write out table in html
pic_table %>%
gt(rowname_col = "trait") %>%
  cols_label(
    n_contrasts = "Num. constrasts",
    n_pos_con = "Num. pos. constrasts",
    statistic = md("*t*"),
    p.value = md("*P*"),
  ) %>% 
  gtsave(here::here("ms/Table_4.html"))

@@

# Write out table in rich text format
correlated_evo_test_table %>%
gt(rowname_col = "trait") %>%
  cols_label(
    logL_indep = "LogL(independent)",
    logL_dep = "LogL(dependent)",
    likelihood_ratio = "Likelihood ratio",
    pval = md("*P*"),
  ) %>% 
  gtsave(here::here("ms/Table_5.html"))
